---
title: "Using the supertrend Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the supertrend Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 7,
  fig.height = 4
)
```

## Overview

`supertrend` adds the SuperTrend technical indicator and its trading
signals to the `quantmod` workflow. The calculation matches what users
see on TradingView: ATR-based bands with a configurable multiplier,
trailing in the direction of the trend until price closes through them.

## Computing the indicator

```{r}
library(supertrend)
data(spy_sample)

st <- SuperTrend(spy_sample, n = 10, multiplier = 3)
head(st, 15)
```

The output xts has four columns:

- `supertrend` — the indicator line
- `trend` — `+1` (uptrend) or `-1` (downtrend)
- `upper_band`, `lower_band` — the trailing bands

## Plotting

```{r}
chartSuperTrend(spy_sample, theme = "white",
                n = 10, multiplier = 3)
```

The line is green during uptrends and red during downtrends. To layer it
onto an existing chart instead, use `addSuperTrend()`:

```{r}
quantmod::chartSeries(spy_sample, theme = "white", name = "SPY (synthetic)")
addSuperTrend(n = 10, multiplier = 3)
```

## Extracting trading signals

```{r}
sig <- supertrend_signals(st)
sig[rowSums(sig) > 0, ]
```

`long_entry`, `short_entry`, `long_exit`, and `short_exit` are 0/1 flags
on flip bars. By construction, `long_entry == short_exit` and
`short_entry == long_exit` — they are exposed separately so they can be
fed to backtesting frameworks (such as `quantstrat`) as independent
rules.

## A trivial signal-following backtest sketch

```{r}
position <- cumsum(as.numeric(sig$long_entry) - as.numeric(sig$short_entry))
position <- ifelse(position > 0, 1, ifelse(position < 0, -1, 0))
returns  <- diff(log(as.numeric(spy_sample$Close)))
strategy_returns <- head(position, -1) * tail(returns, -1)
sum(strategy_returns, na.rm = TRUE)
```

This is a sketch — production backtesting needs entry/exit timing
assumptions, slippage, and position sizing. See `quantstrat` or
`PerformanceAnalytics`.

## Tuning ATR smoothing

The default ATR smoothing is Wilder's (matches TradingView). For SMA or
plain EMA smoothing:

```{r}
SuperTrend(spy_sample, atr_method = "sma")  |> head(15)
SuperTrend(spy_sample, atr_method = "ema")  |> head(15)
```
